Extended Early Adulthood and Attitude Change

### 2024-07-02 manuscript/formative_period_kk.Rmd
clean demo 70, 90, 92

>>>>

For the 1990-92 panel, respondents did not re-report their employment status, marital status, educational attainment, and parental status for the 1991 wave. Respondents who participated in that wave were coded as according to their response in the 1990 wave for these items.

Children:

Broadly speaking, questions tapping marital status tend to capture the same . In contrast, questions tapping the number of children a respondent has vary significantly across panels and even within panels. Specifically, questions occasionally tap how many children are currently living with the respondent and occasionally tap how many children the respondent has ever had. While these items are highly correlated for respondents with young children, these two approaches to the question produce significant differences in rates among parents whose children have left home. They also produce differences among respondents who live in

1990 pre: Number of children in house
1991: copied from 1990
1992: any children?
1992 post: copies from 1992pre
1993: copied from 1992 pre
1994: any children ever
96: Any children under 18 in household
